---
title: "HW2"
author: "Caitlin Bolz"
date: "2/25/2021"
output: word_document
---

```{r warning=FALSE}
library(dplyr)
library(fastDummies)
library(mice)
```
 use mutate
 convert variable to dummy
 then use glm

# Part 1

* Build a logistic regression model to estimate P(RHC). 
* State clearly how you deal with missing values and how you arrive at your logistic model(e.g., how and why you chose the terms, including interactions, if any).
* Give the R code and output for reproducing your logistic fit.

```{r}
rhc = read.table("rhcdata.txt", header = T, row.names = 1)
```

Looking at the structure of the data and which variables have missing values.
```{r}
str(rhc)
sapply(rhc, function(x) sum(is.na(x)))
```


Converting the variables that were characters to become factors. Also turning swang1 (indicator if RHC or noRHC into an integer)
```{r}
rhc1 = rhc %>% 
  mutate(
    cat1 = as.factor(cat1),
    cat2 = as.factor(cat2),
    ca = as.factor(ca),
    sex = as.factor(sex),
    sex = as.integer(sex),
    swang1 = as.factor(swang1),
    dnr1  = as.factor(dnr1),
    resp  = as.factor(resp),
    card  = as.factor(card),
    neuro  = as.factor(neuro),
    gastr  = as.factor(gastr),
    renal  = as.factor(renal),
    meta  = as.factor(meta),
    hema  = as.factor(hema),
    seps  = as.factor(seps),
    trauma  = as.factor(trauma),
    ortho  = as.factor(ortho),
    dnr1  = as.integer(dnr1),
    resp  = as.integer(resp),
    card  = as.integer(card),
    neuro  = as.integer(neuro),
    gastr  = as.integer(gastr),
    renal  = as.integer(renal),
    meta  = as.integer(meta),
    hema  = as.integer(hema),
    seps  = as.integer(seps),
    trauma  = as.integer(trauma),
    ortho  = as.integer(ortho),
    ninsclas = as.factor(ninsclas),
    race = as.factor(race),
    income = as.factor(income),
    swang1 = as.integer(swang1)
    )

str(rhc1)
```


```{r}

init = mice(rhc1, maxit=0) 
meth = init$method
predM = init$predictorMatrix
```

```{r}
set.seed(103)
imputed = mice(rhc1, predictorMatrix = predM, m=5)
```




```{r}
fit1 = glm(swang1 ~ (cat1	+ ca	+ sadmdte	+ dschdte	+ dthdte	+ lstctdte +	death +	cardiohx	+ chfhx	+ dementhx +	psychhx	+ chrpulhx +	renalhx	+ liverhx	+ gibledhx	+ malighx +	immunhx +	transhx	+ amihx	+ age	+ sex	+ edu +	surv2md1 +	das2d3pc +  t3d30 +	dth30	+ aps1 +	scoma1	+ wblc1 +	temp1 +	pafi1 +	alb1 +	hema1	+ bili1	+ crea1 + sod1 +	pot1 + paco21	+ ph1	+  dnr1	+ ninsclas +	resp	+ card +	neuro	+ gastr	+ renal	+ meta	+ hema	+ seps	+ trauma +	ortho	+ adld3p	+ race	+ income +	ptid +	survtime), data = rhc1)
```


```{r}
summary(fit1) # display results
confint(fit1) # 95% CI for the coefficients
exp(coef(fit1)) # exponentiated coefficients
exp(confint(fit1)) # 95% CI for exponentiated coefficients
pred = predict(fit1, type="response") # predicted values
res = residuals(fit1, type="deviance") # predicted residuals
```




# Plotting Important Scores
```{r}
par(las = 1, mar = c(5,5,4,2), cex = .75)

leg.col= c("orange","yellow")
leg.txt = c("highly important","likely important")

x = read.table("imp.scr",header=TRUE)
score = x$Score
vars = x$Variable
type = x$Type

barcol = rep("orange",length(vars))
barcol[type == "L"] = "yellow"
barcol[type == "U"] = "cyan"
n = sum(x$Type != "U")

barplot(rev(score[1:n]), names.arg = rev(vars[1:n]),	col = rev(barcol[1:n]), horiz = T, xlab = "GUIDE Importance Scores", main = "Scores of Important RHC Variables")

abline(v = 1, col = "red", lty = 2)
legend("bottomright", legend = leg.txt, fill = leg.col)

```

# Part 3
What does the logistic model say about the effects of the variables? How does it agree or disagree with the GUIDE tree and importance scores?




# Part 4
Build a GUIDE forest model to estimate P(RHC) and plot the estimates versus those from logistic regression (see slide 54). Say which method is more accurate and why you think so.

R code for Plotting Predicted Probabilities
```{r}
tree = read.table("classpred.txt",header=TRUE)
forest = read.table("forestpred.txt",header=TRUE)
tree.p = tree[,6]
forest.p = forest[,3]
plot(forest.p ~ tree.p, xlab="Tree Predicted Probabilities",
ylab="Forest Predicted Probabilities",col="blue", main = "RHC Prediced Probabitlites of Forest vs Tree")
abline(c(0,1),col="red")
```


# Part 5
Attached to my canvas submission is my input and output files for the GUIDE forest (forestin.txt and forestout.txt) and important scores (impin.txt and impout.txt).

Files I need to include
* impin.txt
* impout.txt
* forestin.txt
* forestout.txt